A generalization of the Bradley-Terry model for draws in chess

### 2020-09-30 inst/curacao1962_threeplayers_rest_monster.Rmd
footnote on difference in games played

```{r}
a <- cbind(a,cncmp_white=0,cncmp_black=0)
for(i in seq_len(nrow(a))){
  r <- a$round[i]
  jj_w <- which(colnames(cumulative_noncollusive_matches)==a$W[i])
  jj_b <- which(colnames(cumulative_noncollusive_matches)==a$B[i])
  ncmp_w <- cumulative_noncollusive_matches[r, jj_w]
  ncmp_b <- cumulative_noncollusive_matches[r, jj_b]
  a$cncmp_white[i] <- ncmp_w
  a$cncmp_black[i] <- ncmp_b
}
head(a)
tail(a)
```

>>>>

```{r}
##  To justify the footnote "No game in the tournament is played
##  between two players with cumulative game count (collusivitity
##  ignored), differ by more than one" in jebo_chess_revision2.tex,
##  replace `cumulative_noncollusive_matches` with
##  `cumulative_matches` in this chunk.
##

a <- cbind(a,cncmp_white=0,cncmp_black=0)
for(i in seq_len(nrow(a))){
  r <- a$round[i]
  jj_w <- which(colnames(cumulative_noncollusive_matches)==a$W[i])
  jj_b <- which(colnames(cumulative_noncollusive_matches)==a$B[i])
  ncmp_w <- cumulative_noncollusive_matches[r, jj_w]
  ncmp_b <- cumulative_noncollusive_matches[r, jj_b]
  a$cncmp_white[i] <- ncmp_w
  a$cncmp_black[i] <- ncmp_b
}
head(a)
tail(a)
```

### 2020-09-30 inst/jebo_chess_revision2.tex
footnote on difference in games played

\textcolor{DarkGreen}{It is reasonable to suppose that collusion of
  the type considered here is ``effective'' in the sense that
  noncollusive games are detrimental to future play in a way that
  collusively drawn games are not.  At the end of the tournament,
  Petrosian, Keres and Geller had each played a total of 18
  noncollusive matches while Fischer, Benko and Filip had played a
  total of 26 or 27 (Tal, retiring mid tournament due to illness,
  played only 21).  For each game in the tournament, we count the
  total noncollusive games played up to that point for both the white
  and black player.  If, in that game, the number of previous
  noncollusive games for the white and black player differs by more
  than one, we posit a ``rest
  monster'' whose strength helps the player who has played fewer
  noncollusive games.}

>>>>

\textcolor{DarkGreen}{It is reasonable to suppose that collusion of
  the type considered here is ``effective'' in the sense that
  noncollusive games are detrimental to future play in a way that
  collusively drawn games are not.  At the end of the tournament,
  Petrosian, Keres and Geller had each played a total of 18
  noncollusive matches while Fischer, Benko and Filip had played a
  total of 26 or 27 (Tal, retiring mid tournament due to illness,
  played only 21).  For each game in the tournament, we count the
  total noncollusive games played up to that point for both the white
  and black player.  If, in that game, the number of previous
  noncollusive games for the white and black player differs by more
  than one\footnote{\textcolor{DarkGreen}{If collusivity is ignored,
    no game in the tournament is played between two players with
    cumulative game count differ by more than one.}}, we posit a ``rest
  monster'' whose strength helps the player who has played fewer
  noncollusive games.}
